---
title: "Modelling Species Distribution in R"
output:
  pdf_document: 
    number_sections: yes
  html_document: 
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

**FOR NOW, THIS IS JUST A BETA TEST**


# Running Maxent in R

** REMEMBER TO MEASURE THE EXECUTION TIMES OF BOTH PROCESSES **

Remember to compair also
1. numeric precision and accuracy
2. easy of use
3. redability and usefulness of output

## Picking a dataset

** TESTING ONLY WITH *Puma_concolor* (smaller dataset) TO SEE IF IT WORKS **

```{r load}
concolor <- readRDS("dados.RDS")$Puma_concolor
```

## Running with the `maxnet` package (which accesses `glmnet` package)

### Running `maxnet()`

<!-- include `, cache=TRUE` later if needed -->
```{r maxnet} 
teste1 <- maxnet::maxnet(p = concolor$P_concolor_P_A, data = concolor[, 2:16])
```

### Presence-absence prediction 

```{r maxnet-predictions} 
concolor %>%
  select(latitude, longitude) %>%
  mutate(predict = dismo::predict(teste1, newdata = concolor[, 2:16], type = "logistic")) %>%
  ggplot(aes(x = longitude, y = latitude, color = predict)) +
  geom_point() +
  coord_fixed() +
  theme(
    axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(),
    axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank()
  )
```

### Response plots for each regressor

```{r maxnet-regressors-plots, warning = FALSE, error = FALSE} 
plot(teste1, vars = names(teste1$samplemeans[1:4]), type = "logistic")
plot(teste1, vars = names(teste1$samplemeans[5:8]), type = "logistic")
plot(teste1, vars = names(teste1$samplemeans[9:12]), type = "logistic")
plot(teste1, vars = names(teste1$samplemeans[13:15]), type = "logistic")
```

### Looking at the object returned by `maxnet()`

```{r maxnet-return} 

names(teste1)
sapply(teste1, class)
sapply(teste1, length) 
sapply(teste1, dim)
```




<!-- ### Saving Estimates to Disk -->

## Running with the `dismo` package (which accesses `Maxent` software directly)


```{r dismo}
teste2 <- dismo::maxent(x = concolor[, 2:16], p = concolor$P_concolor_P_A)
teste2
# plot(teste2)
```


<!-- Check https://stackoverflow.com/questions/35082922/running-maxent-in-r -->

** CHECK IF `dismo` IS PASSING THE CORRECT VALUES FOR THE OPTIONS (see Rafa's mail) **

<!-- ### Saving Estimates to Disk -->

# Comparing the estimates from both methods

<!-- ## Loading the Estimates from `Maxent` Software -->

## Correlation

## Biplots 

