---
title: "Modelling Species Distribution in R"
output:
  pdf_document: 
    number_sections: yes
  html_document: 
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(maxnet)
```

**FOR NOW, THIS IS JUST A BETA TEST**


# Running Maxent in R

** REMEMBER TO MEASURE THE EXECUTION TIMES OF BOTH PROCESSES **

Remember to compair also
1. numeric precision and accuracy
2. easy of use
3. redability and usefulness of output

## Picking a dataset

** TESTING ONLY WITH *Puma_concolor* (smaller dataset) TO SEE IF IT WORKS **

```{r load}
concolor <- readRDS("dados.RDS")$Puma_concolor
```

## Running with the `maxnet` package (which accesses `glmnet` package)

<!-- include `, cache=TRUE` later if needed -->
```{r maxnet} 
teste1 <- maxnet(p = concolor$P_concolor_P_A, data = concolor[, 2:16])
teste1
# plot(teste1)
```

<!-- ### Saving Estimates to Disk -->

## Running with the `dismo` package (which accesses `Maxent` software directly)


<!-- ```{r dismo}  -->
<!-- teste2 <- ???(p = concolor$P_concolor_P_A, data = concolor[, 2:16]) -->
<!-- teste2 -->
<!-- plot(teste1) -->
<!-- ``` -->


<!-- Check https://stackoverflow.com/questions/35082922/running-maxent-in-r -->

** CHECK IF `dismo` IS PASSING THE CORRECT VALUES FOR THE OPTIONS (see Rafa's mail) **

<!-- ### Saving Estimates to Disk -->

# Comparing the estimates from both methods

<!-- ## Loading the Estimates from `Maxent` Software -->

## Correlation

## Biplots 

